## Analysis for {{island}}


```{r}
#| echo: false
peng_data <- penguins |> 
    filter(species == params$species & island =="{{island}}")  |> 
    drop_na()

```

::: {#tbl-penguins-{{island}}}
```{r}
#| echo: false
modelsummary::datasummary(sex*(body_mass_g + bill_length_mm + bill_depth_mm)~(N+mean+sd), data=peng_data)

```
Summary statistics for penguins on {{island}}
:::


::: {#fig-penguins-{{island}}}
```{r}
#| echo: false
#| label: penguins-{{island}}
ggplot(peng_data, aes(x=bill_length_mm, y=bill_depth_mm,fill = sex)) +
  geom_point(shape=21, size=3, alpha=0.7) +
  labs(
    x = "Bill Length (mm)",
    y = "Bill Depth (mm)",
  )
```
Scatter plot of bill dimensions for penguins on {{island}}
:::

The summary statistics of penguins on {{island}} is given in @tbl-penguins-{{island}} and a scatter plot of bill dimensions is shown in @fig-penguins-{{island}}.

Next, we fit a linear model to predict bill depth from bill length and sex of the penguins on {{island}}. The results are summarized below in @tbl-model-{{island}}.

::: {#tbl-model-{{island}}}
```{r}
#| echo: false
model <- lm(bill_depth_mm ~ bill_length_mm+sex, data=peng_data)
modelsummary(model)
```
Regression results for penguins on {{island}}
:::
