---
title: "Penguins"
format: 
  html: default
  typst:
    template-partials:  
      - typst-show.typ
      - typst-template.typ
params:
  species: Gentoo
echo: false
message: false
warning: false
author: Nithin
    
---
```{r}
#| include: false
library(glue)
library(tidyverse)
library(palmerpenguins)
library(kableExtra)
library(gghighlight)
library(quarto)
library(modelsummary)

```
```{r}
#| output: asis
#| echo: false
write_yaml_metadata_block(params = list(species = params$species))

# cat(sprintf("\n\n---\nspecies: %s\n---\n\n", params[["species"]]))
```
```{r}
#| include: false
# Define species color schemes

species_colors <- data.frame(
  species = c("Adelie", "Chinstrap", "Gentoo"),
  primary = c("#FF6B35", "#7209B7", "#0D2C54"),
  secondary = c("#004E89", "#F72585", "#339989"),
  stringsAsFactors = FALSE
)

color <- case_when(params$species == "Adelie" ~ "#FF6600",
                   params$species == "Gentoo" ~ "#047075",
                   params$species == "Chinstrap" ~ "#C25BCC")

current_colors <- species_colors[species_colors$species == params$species, ]
sidebar_color <- current_colors$primary
header_color <- current_colors$secondary

```


```{=typst}

#set page(background: place(
        top,
        rect(
            width: 2cm,
            height: 100%,
            fill: rgb(`r shQuote(sidebar_color)`)
        )
    ),
    footer: context [
  *Design: #text(fill: rgb(`r shQuote(header_color)`))[{{< meta author >}}]*
  #h(1fr)
  #counter(page).display(
    "1/1",
    both: true,
  )
]
    )
#h(-1cm)
    #box(
        fill: rgb(`r shQuote(header_color)`),
        width: 0.4fr,
        inset: 10pt,
    )[
        #text(size: 2.5em, fill: white)[*{{< meta title >}}*]
    ]

*#text(size: 1.2em)[Species: `{r} params[["species"]]`]* 
 
```

The `r params$species` penguins can be found on the island(s) of: `r glue_collapse(penguins |> filter(species == params$species) |> count(island) |> pluck(1), sep = ", ", last = ", and ")`. The total number of `r params$species` penguins in the dataset is `r penguins |> filter(species == params$species) |> nrow()`.

Let us analyse the `r params$species` penguins by island. The results for each island are shown below.


```{r}
#| include: false

islands <- penguins |> filter(species == params$species) |> distinct(island) |> arrange(island) |> pull()

expanded <- map(islands, function(island){
    knitr::knit_expand(
        text = c(
  "## Analysis for {{island}}",
  "",
  "```{r}",
  "#| echo: false",
  "peng_data <- penguins |> ",
  "  filter(species == params$species & island == \"{{island}}\") |> ",
  "  drop_na()",
  "```",
  "",
  "::: {#tbl-penguins-{{params$species}}-{{island}}}",
  "```{r}",
  "#| echo: false",
  "modelsummary::datasummary(",
  "  sex*(body_mass_g + bill_length_mm + bill_depth_mm) ~ (N+mean+sd),",
  "  data = peng_data",
  ")",
  "```",
  "Summary statistics for penguins on {{island}}",
  ":::",
  "",
  "```{r}",
  "#| echo: false",
  "#| label: fig-penguins-{{params$species}}-{{island}}",
  "#| fig-cap: 'Scatter plot of bill dimensions for penguins on {{island}}'",
  "ggplot(peng_data, aes(x=bill_length_mm, y=bill_depth_mm, fill=sex)) +",
  "  geom_point(shape=21, size=3, alpha=0.7) +",
  "  labs(",
  "    x = 'Bill Length (mm)',",
  "    y = 'Bill Depth (mm)'",
  "  )",
  "```",
  "",
  "The summary statistics of penguins on {{island}} is given in @tbl-penguins-{{params$species}}-{{island}} ",
  "and a scatter plot of bill dimensions is shown in @fig-penguins-{{params$species}}-{{island}}.",
  "",
  "Next, we fit a linear model to predict bill depth from bill length and sex of the penguins on {{island}}. ",
  "The results are summarized below in @tbl-model-{{params$species}}-{{island}}.",
  "",
  "::: {#tbl-model-{{params$species}}-{{island}}}",
  "```{r}",
  "#| echo: false",
  "model <- lm(bill_depth_mm ~ bill_length_mm + sex, data=peng_data)",
  "modelsummary(model)",
  "```",
  "Regression results for penguins on {{island}}",
  ":::"
),
        island=island
    )

}
)  |> 
    flatten()
parsed_child <- knitr::knit_child(text = unlist(expanded))
```

`r parsed_child`

